---
output: github_document

---



#                   ClusteringR

<!-- badges: start -->
  <!-- badges: end -->

  Its functionality includes exploratory data analysis, data segmentation and data visualization.It is designed to handle realistic data sets : hedonic data set and sensory data set.
It makes use of several clustering methods as well as the implementation of partition-validity approach.

Finally, a graphical user interface is implemented  with R shiny in order to propose a user friendly package.


## Installation

``` r
install.packages("devtools")
devtools::install_github("BouzidiImen/ClusteringR")

```


## Usage 
Below is a quick look at how ClusteringR can help to do your sensory analysis.
Diverse methods of clustering are available in the ClusteringR package :

'Hierarchical','Diana','Kmeans','Clara','Pam','Sota' and 'Som'

```{r include=FALSE}
library(ClusteringR)
library(cowplot)# to use plot_grid
```



```{r}

library(ClusteringR)
# Create a clustering object  -------------------------------------------------
cl <- Clustering(t(hedo),ClustMeth='Hierarchical',k=4,Hdismethod='euclidean',Hmethod="ward.D2",
                    Graph=F,VarCart=F,IndCart=F,ElbowP=F )
#Plot of elbow method , dendrogram , variables representation and individuals

plot_grid(cl$ElbowP, cl$dendrogram, cl$Pvar, cl$Pind, hjust = 1, vjust = 1,
          scale = c(1, 1, 1, 1))





```



## Data available in the package

* senso: sensory data from a professional trial of 8 biscuits by 12 judges.
* hedo: hedonic data from a trial of 8 biscuits by 294 customers.
```{r}
#Usage 
library(ClusteringR)
S=senso # sensory data 
H=hedo # hedonic data

```

## A User Friendly Package

Within the package you find a shiny application that demonstrate what the package does.
```{r eval=FALSE}
ClustShiny() #run shiny application
```


P.S.You can visit the following link to get a sneak peek on the package functionalities.

[Shiny application for the package](https://imenbouzidi.shinyapps.io/InterfaceForThepackage/)
